A Distributed Segment-based Approach for Topology-agnostic Nano Networks Routing

### 2013-08-18 PAPER/introduction.tex
[NanoTask-2] Completed TODOs 2-12. Updated bibliography and introduction

In the last years, Self-assembled nanoscale architectures~\cite{TODO2}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{TODO3}.
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and nanotubes~\cite{TODO4}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold (see figure~\ref{fig:dna_tag}.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
  \caption{DNA tag matching}
  \label{fig:dna_tag}
\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{TODO5}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: (i)limited node complexity, (ii) large scale
randomness and (iii) high defect rates.

@@

These aspects of a DNA-self assembly process lead to some important
architectural implications to be addressed when approaching to the
Computer Design: computational model must be founded on a distributed
network of small computing and storage nodes, randomly placed and
interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
can be found in~\cite{TODO6}, where instructions and data operands travel
on packets and routed using a topology-agnostic strategy that avoids
deadlock, since no particular regularity can be assumed in such
network.

@@

Several works~\cite{TODO7} have been presented addressing the problem of topology
agnostic routing. While they show interesting
performances, the requirement for virtual channels resources 
to avoid deadlock makes them not suitable for the specific DNA self
assembled networks we are assuming as background.
Other topology independent algorithms~\cite{TODO8} don't use virtual channels to
achieve deadlock freedom, but turn proibitions. 
In particular, up*/down* exploits the creation of a spanning tree of the
topology, then placing bidirectional restrictions by avoiding a packet
to traverse the same link in both up and down directions.
While the hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{TODO9} mitigate this
issue, but the set of turn restrictions is still prefixed,
striclty depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{TODO10} or the
location~\cite{TODO11} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{TODO12}.

>>>>

In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}.
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and nanotubes~\cite{bachtold2001, tans1998, cui2001}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold (see figure~\ref{fig:dna_tag}.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
  \caption{DNA tag matching}
  \label{fig:dna_tag}
\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: (i)limited node complexity, (ii) large scale
randomness and (iii) high defect rates.

@@

These aspects of a DNA-self assembly process lead to some important
architectural implications to be addressed when approaching to the
Computer Design: computational model must be founded on a distributed
network of small computing and storage nodes, randomly placed and
interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
can be found in~\cite{patwardhan2006_1}, where instructions and data operands travel
on packets and routed using a topology-agnostic strategy that avoids
deadlock, since no particular regularity can be assumed in such
network.

@@

Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
agnostic routing. While they show interesting
performances, the requirement for virtual channels resources 
to avoid deadlock makes them not suitable for the specific DNA self
assembled networks we are assuming as background.
Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} don't use virtual channels to
achieve deadlock freedom, but turn proibitions. 
In particular, up*/down* exploits the creation of a spanning tree of the
topology, then placing bidirectional restrictions by avoiding a packet
to traverse the same link in both up and down directions.
While the hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches such as
FX~\cite{sancho2000} mitigate this
issue, but the set of turn restrictions is still prefixed,
striclty depending on the particular tree root selected. 
Other solutions try to approach the issue of irregular
topologies by limiting the number~\cite{dally1994, duato1997, gomez2004, koibuchi2008} or the
location~\cite{zhang2008, sui2000, flich2008, liu2011} of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006}.
